Using Optical Character Recognition in an Applied Research Workflow

### 2020-12-12 outputs/documents/paper.Rmd
Add abstract and high-level descriptions of kindai and tesseract

---
title: "Notes and approaches to OCR"
author: "Rohan Alexander, John Tang, Diego Mamanche Castellanos"
date: "8 December 2020"
abstract: "TBD"
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: false
bibliography: references.bib
---

@@

A crucial step in the data analysis workflow is gathering data. This step involves tools and methods to collect raw data in an systematic way. In this paper we are interested in gathering data from Portable Document Format (PDF) files, in particular, when these PDFs were created by scans, and hence must be processed before the data they contain can be prepared, cleaned, and analysed. Such PDF files are generally unstructured data, meaning that the data are not tagged nor organised in a regular way.^[Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset. Some examples are tables and relations. Semi-structured data contains this same information, but instead of having regular structures applied to all items in the dataset, the data might be interpreted with structural information. It can be supplied as tags e.g. name = "Bob" but also other markers to separate semantic elements and enforce hierarchies of records and fields within the data. Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags. However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data [@Losee2006]. This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags in the form of a text replacement for each character image could be assigned manually, typically a statistical model is used for reasons of efficiency and reproducibility, and this process is called Optical Character Recognition (OCR). We evaluate several pre-trained commercial OCR options accessed via APIs: 1) X, 2), Y and 3) Z; additionally several pre-trained OCR options that we run ourselves: 4) X, 5), Y and 6) Z ; and finally 7) training and running our own model. We find... **[TBD]**.

@@

@@

**DIEGO - what is this?**.
; the text should be available for full-text information retrieval; the text is to be coded in HTML or SGML; the text should be available to adaptive equipment for the visually impaired; the file size is of concern (in terms of storage or bandwidth to transmit); or the resources are available to perform OCR and correct the output.

@@

In this section we introduce the OCR options that we consider, they essential features and cost.

There are seven OCR options evaluated in this study (Table \@ref(tab:tableofoptions)).

@@

**Add paragraph about each.**

@@

3:

@@

12: Anh Duc Le, Daichi Mochihashi, Katsuya Masuda, Hideki Mima, and Nam Tuan Ly. 2019. Recognition of Japanese historical text lines by an attention-based encoder-decoder and text line generation. In Proceedings of the 5th International Workshop on Historical Document Imaging and Processing (HIP ’19). Association for Computing Machinery, New York, NY, USA, 37–41. DOI:https://doi.org/10.1145/3352631.3352641

>>>>

---
title: "Using Optical Character Recognition in an Applied Research Workflow"
author:
  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca.]
  - John Tang^[University of Melbourne.]
  - Diego Mamanche Castellanos^[University of Toronto.]
date: "12 December 2020"
abstract: "We discuss the use of Optical Character Recognition (OCR) as a initial step in an applied research workflow. OCR is a way of converting images, for instance in a PDF file, into text and numbers that can then be analysed. We review a variety of methods and their relative merit. The choice between these approaches turns on the scale of the OCR required, the level of funding that is available, and the user's technical skills. We provide a hueristic to guide this decision and worked examples. Finally, we place this within the context of an illustrative applied research workflow detailing its relationship with other aspects of the workflow."
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: false
bibliography: references.bib
---

@@

A crucial step in the data analysis workflow is gathering data. This step involves tools and methods to collect raw data in an systematic way. In this paper we are interested in gathering data from Portable Document Format (PDF) files, in particular, when these PDFs were created by scans, and hence must be processed before the data they contain can be prepared, cleaned, and analysed. Such PDF files are generally unstructured data, meaning that the data are not tagged nor organised in a regular way.^[Structured data is organized in a highly regular manner or a pre-defined data model where the regularities apply to all the data in a particular dataset. Some examples are tables and relations. Semi-structured data contains this same information, but instead of having regular structures applied to all items in the dataset, the data might be interpreted with structural information. It can be supplied as tags e.g. name = "Bob" but also other markers to separate semantic elements and enforce hierarchies of records and fields within the data. Unstructured data, such as texts or images, holds information with no explicit structured data, such as tags. However, these tags may be assigned using manual or automatic techniques, converting the unstructured data to semi-structured data [@Losee2006]. This diversity and complexity of data structures complicate, even more, the data gathering process as each data type may require a specific gathering approach(es) when needed.] While tags in the form of a text replacement for each character image could be assigned manually, typically a statistical model is used for reasons of efficiency and reproducibility, and this process is called Optical Character Recognition (OCR). We evaluate several pre-trained commercial OCR options accessed via APIs: 1) **X**, 2) **Y**, and 3) **Z**; additionally several pre-trained OCR options that we run ourselves: 4) **X**, 5) **Y**, and 6) **Z**; and finally 7) training and running our own model. We find... **[TBD]**.

@@

Our paper is similar to @Rychlik2020 which focuses on Pashto, Farsi, and Traditional Chinese.

@@

@@

In this section we introduce the OCR options that we consider, their essential features, and cost. There are **seven** OCR options evaluated in this study (Table \@ref(tab:tableofoptions)).

@@

Amazon Rekognition is a proprietary

Amazon Textract

Azure Cognitive Services

Google Vision

Kindai OCR [@Le2019] - https://github.com/ducanh841988/Kindai-OCR - is a pre-trained model that uses an attention based encoder-decoder approach specifically designed for Japanese historical documents. It is part of a larger research program on Japanese character recognition including @Horiuchi2009 and @Nguyen2017. This research program is complementary to research on historical Hanja (Korean) documents, for instance @Kim2004, and  historical Khmer (Cambodia) documents, for instance @Valy2020. @Le2019b provides broader consideration of issues with the recognition of historical Japanese, and related, characters including 'noised, damaged characters, and background', as well as the possibility that characters may be 'written in cursive and are connected'. The Center for Open Data in the Humanities - http://codh.rois.ac.jp - provides a large number of training datasets, and runs the n2i Project from which Kindai came out of. @Narang2020 provides an overview.

Kraken

Tesseract **[ADD CITE]** - https://github.com/tesseract-ocr/tesseract - is an open-source OCR engine initially developed 'at HP between 1985 and 1995, shelved for 10 years, open-sources in 2006 and now developed mostly at Google' [@Smith2013]. It has had a variety of versions, with the latest being Tesseract 4 which added a 'neural net (LSTM) based OCR engine' [@tesseract2018]. Tesseract is a widely used OCR engine with a variety of implementations available including the default usage of command line, Python through the pytesseract package **[ADD CITE]** and R through the tesseract package [@Ooms2019] for which a useful starter example is @Rodrigues2019.

There are two additional approaches that researchers may also consider: manual and roll-your-own. In the manual approach, teams of research assistants are paid to inspect each page and input the correct element. This is likely the gold-standard in terms of accuracy, however it is only approach for smaller datasets, and is not reproducible. Finally, as the statistics underlying the approaches mentioned above are within the capacity of many researchers it is tempting to conclude that one should write one's own OCR engine. Don't do this.

@@

@@
